Blockchain System

### 2020-12-09 papers/execution-model/model.tex
Add files via upload

\begin{mathpar}
  \inferrule[Node-Op']
    {
    \Angle{\PAK,\OP.\PUK} \in \ACCOUNTS
  }{
    [\EC\OP :: \EXPRS, \ACCOUNTS, \OPERATIONS] \NodeTrans{}
    [\EXPRS, \ACCOUNTS, (\EC{},\OP):: \OPERATIONS]
  }
\end{mathpar}

\begin{mathpar}
  \inferrule[Node-Inject']{
    \CHECKBAL (\MANAGERS, \PUK, \NTEZ, \MTEZ) \\
    \CHECKCOU (\MANAGERS, \PUK) \\
    \CHECKPUB (\MANAGERS, \PUK') \\
    \CHECKGAS (\PUK, \PUK', \NTEZ, \MTEZ) \\
    \OP = \TRANSFER\NTEZ\PUK{\PUK'}\MTEZ \\
    \OPH = \GENERATEOPH (\PUK, \PUK', \NTEZ, \MTEZ, \TIME)
  }{
   { [\EXPRS, \ACCOUNTS, (\EC{},\OP) :: \OPERATIONS] \| [\PENDING,
     \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME] } \SystemTrans \\
   { [\EC{\OPH}  :: \EXPRS, \ACCOUNTS, \OPERATIONS] \|
     [ \Angle{\OP,\OPH, \TIME}
     ::\PENDING,
     \ACCEPTED,
     \UPDATECOU(\MANAGERS, \PUK, \TRUE),
     \CONTRACTORS,
     \TIME]
   }
  }
\end{mathpar}

\begin{mathpar}
  \inferrule[Block-Accept'']{
    \OP = \TRANSFER\NTEZ\PUK{\PUK'}\MTEZ \\
    \TIME'-\TIME < 60
  }{
    { % [\EC{?\OPH}  :: \EXPRS, \ACCOUNTS, \OPERATIONS] \|
      [\Angle{\OP,\OPH, \TIME} :: \PENDING, \ACCEPTED, \MANAGERS,
      \CONTRACTORS, \TIME']}
    \BlockTrans  \\
    { % [\EC{\OPH}  :: \EXPRS, \ACCOUNTS, \OPERATIONS] \|
      [\PENDING, \Angle{\OP,\OPH, \TIME,\TIME'} :: \ACCEPTED,
      \UPDATESUCC(\MANAGERS, \PUK, \PUK', \NTEZ, \MTEZ),
      \CONTRACTORS, \TIME'+1]}
  }
\end{mathpar}

\begin{mathpar}
  \inferrule[Block-Timeout'']{
    \OP = \TRANSFER[\STRING]\NTEZ\PUK\ADDR\MTEZ \\
    \TIME'-\TIME \ge 60
  }{ % [\EC{?\OPH}  :: \EXPRS, \ACCOUNTS, \OPERATIONS] \|
    {[\Angle{\OP,\OPH, \TIME} :: \PENDING, \ACCEPTED, \MANAGERS,
      \CONTRACTORS, \TIME']}
    \BlockTrans 
    { % [\EC{\RAISE timeout}  :: \EXPRS, \ACCOUNTS, \OPERATIONS] \|
      [\PENDING, \ACCEPTED, \UPDATECOU(\MANAGERS, \PUK, \FALSE),
      \CONTRACTORS, \TIME']}
  }
\end{mathpar}

@@

\begin{mathpar}
  \inferrule[Node-Op]
  {
    \Angle{\PAK,\OP.\PUK} \in \ACCOUNTS
  }{
    [\EXPRS, \ACCOUNTS, \OPERATIONS]
    \NodeTrans{}
    [\EXPRS, \ACCOUNTS, \OP:: \OPERATIONS]
  }

  \inferrule[Node-Oph]
  {
   \\
  }{
    [\EC\OP :: \EXPRS, \ACCOUNTS, \OPERATIONS]
    \NodeTrans{}
    [\EC\OPH :: \EXPRS, \ACCOUNTS, \OPERATIONS]
  }

  \inferrule[Node-System]
  {\NODE \NodeTrans \NODE'}
  { {\NODE :: \overline\NODE \| \BLOCKCHAIN}
    \SystemTrans
    {\NODE' :: \overline\NODE \| \BLOCKCHAIN}}

@@

\subsection{Transfers}

\begin{mathpar}
  \inferrule{
    \CHECKBAL (\MANAGERS, \PUK, \NTEZ, \MTEZ) \\
    \CHECKCOU (\MANAGERS, \PUK) \\
    \CHECKPUB (\MANAGERS, \PUK') \\
    \CHECKGAS (\PUK, \PUK', \NTEZ, \MTEZ) \\
    \OP = \TRANSFER\NTEZ\PUK{\PUK'}\MTEZ \\
    \OPH = \GENERATEOPH (\PUK, \PUK', \NTEZ, \MTEZ, \TIME)
  }{
   { [\ACCOUNTS, \OP :: \OPERATIONS] \| [\PENDING,
     \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME] } \SystemTrans \\
   { [\ACCOUNTS, \OPERATIONS] \|
     [ \Angle{\OP,\OPH, \TIME}
     ::\PENDING,
     \ACCEPTED,
     \UPDATECOU(\MANAGERS, \PUK, \TRUE),
     \CONTRACTORS,
     \TIME]
   }
  }
\end{mathpar}
~\\
~\\
Rule 2 [rejected of counter]:
\begin{mathpar}
  \inferrule{
    %\NEG\ \CHECKCOU (\MANAGERS, \PUK)\\
    %\OP = \TRANSFER\NTEZ\PUK{\PUK'}\MTEZ \\
    \NEG\ \CHECKCOU (\MANAGERS, \PUK) \\
    \OP = \TRANSFER\NTEZ\PUK{\PUK'}\MTEZ \\
  }{
   { [\ACCOUNTS, \OP :: \OPERATIONS] \| [\PENDING,
     \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME] } \SystemTrans
   { [\ACCOUNTS, \OPERATIONS] \|
     [ \PENDING,
     \ACCEPTED,
     \MANAGERS,
     \CONTRACTORS,
     \TIME]
   }
  }
\end{mathpar}
~\\
~\\
Rule 3 [rejected of balance]:
\begin{mathpar}
  \inferrule{
    \NEG\ \CHECKBAL (\MANAGERS, \PUK, \NTEZ, \MTEZ) \\
    \OP = \TRANSFER\NTEZ\PUK{\PUK'}\MTEZ \\
  }{
   { [\ACCOUNTS, \OP :: \OPERATIONS] \| [\PENDING,
     \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME] } \SystemTrans
   { [\ACCOUNTS, \OPERATIONS] \|
     [ \PENDING,
     \ACCEPTED,
     \MANAGERS,
     \CONTRACTORS,
     \TIME]
   }
  }
\end{mathpar}
~\\
~\\
Rule 4 [rejected of public key]:
\begin{mathpar}
  \inferrule{
    \NEG\ \CHECKPUB (\MANAGERS, \PUK') \\
    \OP = \TRANSFER\NTEZ\PUK{\PUK'}\MTEZ \\
  }{
   { [\ACCOUNTS, \OP :: \OPERATIONS] \| [\PENDING,
     \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME] } \SystemTrans
   { [\ACCOUNTS, \OPERATIONS] \|
     [ \PENDING,
     \ACCEPTED,
     \MANAGERS,
     \CONTRACTORS,
     \TIME]
   }
  }
\end{mathpar}
~\\
~\\
Rule 5 [rejected of fee]:
\begin{mathpar}
  \inferrule{
    \NEG\ \CHECKGAS (\PUK, \PUK', \NTEZ, \MTEZ) \\
    \OP = \TRANSFER\NTEZ\PUK{\PUK'}\MTEZ \\
  }{
   { [\ACCOUNTS, \OP :: \OPERATIONS] \| [\PENDING,
     \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME] } \SystemTrans
   { [\ACCOUNTS, \OPERATIONS] \|
     [ \PENDING,
     \ACCEPTED,
     \MANAGERS,
     \CONTRACTORS,
     \TIME]
   }
  }
\end{mathpar}
~\\
~\\
Rule 6 [included]:
\begin{mathpar}
  \inferrule[Block-Accept]{
    \OP = \TRANSFER\NTEZ\PUK{\PUK'}\MTEZ \\
    \TIME'-\TIME < 60
  }{
    {[\Angle{\OP,\OPH, \TIME} :: \PENDING, \ACCEPTED, \MANAGERS,
      \CONTRACTORS, \TIME']}
    \BlockTrans  \\
    {[\PENDING, \Angle{\OP,\OPH, \TIME,\TIME'} :: \ACCEPTED,
      \UPDATESUCC(\MANAGERS, \PUK, \PUK', \NTEZ, \MTEZ),
      \CONTRACTORS, \TIME'+1]}
  }
\end{mathpar}
Rule 7 [timeout]: (applies to both, implicit transfers and contract invocations)
\begin{mathpar}
  \inferrule[Block-Timeout]{
    \OP = \TRANSFER[\STRING]\NTEZ\PUK\ADDR\MTEZ \\
    \TIME'-\TIME \ge 60
  }{
    {[\Angle{\OP,\OPH, \TIME} :: \PENDING, \ACCEPTED, \MANAGERS,
      \CONTRACTORS, \TIME']}
    \BlockTrans
    {[\PENDING, \ACCEPTED, \UPDATECOU(\MANAGERS, \PUK, \FALSE),
      \CONTRACTORS, \TIME']}
  }
\end{mathpar}

\subsection{Smart Contracts}
A. Originate
~\\
~\\
Rule 1 [injected]:
  \inferrule[Block-Originate]{
    \CHECKGAS (\CODE, \INIT, \NTEZ, \MTEZ)  \\
    \CHECKPRG (\CODE, \STRING) \\\\
    \OP = \ORIGINATE\NTEZ\PUK\CODE\STRING\MTEZ \\
    \OPH = \GENERATEOPH(\PUK, \CODE, \NTEZ, \MTEZ, \STRING,\TIME) 
    [
      \ACCOUNTS, \OP :: \OPERATIONS
      ] \| [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME] \to \\
    [\ACCOUNTS, \OPERATIONS] \|
      [\Angle{\OP, \OPH,\TIME} :: \PENDING, \ACCEPTED, \UPDATECOU(\MANAGERS,\PUK,\TRUE), \CONTRACTORS, \TIME]
Rule 2 [rejected of code]:
    \NEG\ \CHECKPRG (\CODE, \STRING) \\
    \OP = \ORIGINATE\NTEZ\PUK\CODE\STRING\MTEZ
    [
      \ACCOUNTS, \OP :: \OPERATIONS
      ] \| [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME] \to 
    [\ACCOUNTS, \OPERATIONS] \|
Rule 3 [rejected of counter]:
    \OP = \ORIGINATE\NTEZ\PUK\CODE\STRING\MTEZ
    [
      \ACCOUNTS, \OP :: \OPERATIONS
      ] \| [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME] \to
    [\ACCOUNTS, \OPERATIONS] \|
Rule 4 [rejected of balance]:
    \OP = \ORIGINATE\NTEZ\PUK\CODE\STRING\MTEZ
    [
      \ACCOUNTS, \OP :: \OPERATIONS
      ] \| [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME] \to 
    [\ACCOUNTS, \OPERATIONS] \|
Rule 5 [rejected of fee]:
    \NEG\ \CHECKGAS (\CODE, \INIT, \NTEZ, \MTEZ) \\
    \OP = \ORIGINATE\NTEZ\PUK\CODE\STRING\MTEZ
    [
      \ACCOUNTS, \OP :: \OPERATIONS
      ] \| [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME] \to 
    [\ACCOUNTS, \OPERATIONS] \|
Rule 6 [included]:
  \inferrule[Block-Accept]{
    \OP = \ORIGINATE\NTEZ\PUK\CODE\STRING\MTEZ \\
      [\Angle{\OP, \OPH,\TIME} :: \PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME']
      [\PENDING, \Angle{\OP, \OPH,\TIME,\TIME'} ::  \ACCEPTED, \UPDATESUCC
      (\MANAGERS, \PUK, \NTEZ, \MTEZ), \\ \Angle{\GENERATEHASH(\CODE, \INIT, \TIME, \TIME'), \NTEZ, \CODE, \STRING} :: \CONTRACTORS, \TIME'+1]
Rule 7 [timeout]:
  \inferrule[Block-Timeout]{
    \OP = \ORIGINATE\NTEZ\PUK\CODE\STRING\MTEZ \\
    \TIME'-\TIME \ge 60
    %\Angle{[\ACCOUNTS, \OPERATIONS, \CONTRACTS],
      [\Angle{\OP, \OPH,\TIME} :: \PENDING, \ACCEPTED, \MANAGERS,
    %}
    \BlockTrans
    % \Angle{[\ACCOUNTS, \OPERATIONS, \CONTRACTS],
      [\PENDING, \ACCEPTED, \UPDATECOU(\MANAGERS,\PUK,\FALSE), \CONTRACTORS, \TIME']
    % }

@@

  }{[\ACCOUNTS, \OP :: \OPERATIONS] \|

@@

    [\ACCOUNTS, \OPERATIONS] \|

@@

    [\ACCOUNTS, \OPERATIONS] \|

@@

    \NodeTrans [\epsilon[\BAL] ::\EXPRS, \ACCOUNTS, \OPERATIONS]  \| \BLOCKCHAIN}

@@

    \NodeTrans [\epsilon[\STORAGE] ::\EXPRS, \ACCOUNTS, \OPERATIONS]  \| \BLOCKCHAIN}

@@

    \NodeTrans [\epsilon[\CODE] ::\EXPRS, \ACCOUNTS, \OPERATIONS]  \| \BLOCKCHAIN}

@@

    \NodeTrans [\epsilon[\COU] ::\EXPRS, \ACCOUNTS, \OPERATIONS]  \| \BLOCKCHAIN}

@@

Query 6 [status-pending]:

@@

      [\Angle{\OP, \OPH, \TIME} :: \PENDING, \ACCEPTED,  \MANAGERS, \CONTRACTORS, \TIME]

@@

    \NodeTrans [\epsilon[\STATUSPENDING] ::\EXPRS, \ACCOUNTS, \OPERATIONS]  \| \BLOCKCHAIN}

@@

Query 7 [status-including]:

@@

      [\PENDING, \Angle{\OP, \OPH, \TIME, \TIME'} :: \ACCEPTED,  \MANAGERS, \CONTRACTORS, \TIME]

@@

    \NodeTrans [\epsilon[\STATUSINCLUDING] ::\EXPRS, \ACCOUNTS, \OPERATIONS]  \| \BLOCKCHAIN}

@@

\section{Functions}
\begin{enumerate}
    \item Function \CHECKPUB (\PUK, \MANAGERS)\ checks whether a public key \PUK\ exists in \MANAGERS.
    \item Function \CHECKPUH (\PUH, \CONTRACTORS)\ checks whether a public hash \PUH\ exists in \CONTRACTORS.
    \item Function \CHECKBAL (\MANAGERS, \PUK, \NTEZ, \MTEZ) checks whether the balance of the account that associates with the public key \PUK\ is greater or equal to \NTEZ\ plus \MTEZ.
    \item Function \CHECKCOU (\MANAGERS, \PUK)\ checks whether the current counter of an account that associates with the public key \PUK\ is unlocked (its flag is False).

>>>>

\begin{mathpar}
  \inferrule[Node-Op]
    {
    \Angle{\PAK,\OP.\PUK} \in \ACCOUNTS
  }{
    [\EC\OP :: \EXPRS, \ACCOUNTS, \OPERATIONS] \NodeTrans{}
    [\EXPRS, \ACCOUNTS, (\EC{},\OP):: \OPERATIONS]
  }
\end{mathpar}

\begin{mathpar}
  \inferrule[Node-Inject]{
    \CHECKBAL (\MANAGERS, \PUK, \NTEZ, \MTEZ) \\
    \CHECKCOU (\MANAGERS, \PUK) \\
    \CHECKPUB (\MANAGERS, \PUK') \\
    \CHECKGAS (\PUK, \PUK', \NTEZ, \MTEZ) \\
    \OP = \TRANSFER\NTEZ\PUK{\PUK'}\MTEZ \\
    \OPH = \GENERATEOPH (\PUK, \PUK', \NTEZ, \MTEZ, \TIME)
  }{
   { [\EXPRS, \ACCOUNTS, (\EC{},\OP) :: \OPERATIONS] \| [\PENDING,
     \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME] } \SystemTrans \\
   { [\EC{\OPH}  :: \EXPRS, \ACCOUNTS, \OPERATIONS] \|
     [ \Angle{\OP,\OPH, \TIME}
     ::\PENDING,
     \ACCEPTED,
     \UPDATECOU(\MANAGERS, \PUK, \TRUE),
     \CONTRACTORS,
     \TIME]
   }
  }
\end{mathpar}

\begin{mathpar}
  \inferrule[Block-Accept]{
    \OP = \TRANSFER\NTEZ\PUK{\PUK'}\MTEZ \\
    \TIME'-\TIME < 60
  }{
    { % [\EC{?\OPH}  :: \EXPRS, \ACCOUNTS, \OPERATIONS] \|
      [\Angle{\OP,\OPH, \TIME} :: \PENDING, \ACCEPTED, \MANAGERS,
      \CONTRACTORS, \TIME']}
    \BlockTrans  \\
    { % [\EC{\OPH}  :: \EXPRS, \ACCOUNTS, \OPERATIONS] \|
      [\PENDING, \Angle{\OP,\OPH, \TIME,\TIME'} :: \ACCEPTED,
      \UPDATESUCC(\MANAGERS, \PUK, \PUK', \NTEZ, \MTEZ),
      \CONTRACTORS, \TIME'+1]}
  }
\end{mathpar}

\begin{mathpar}
  \inferrule[Block-Timeout]{
    \OP = \TRANSFER[\STRING]\NTEZ\PUK\ADDR\MTEZ \\
    \TIME'-\TIME \ge 60
  }{ % [\EC{?\OPH}  :: \EXPRS, \ACCOUNTS, \OPERATIONS] \|
    {[\Angle{\OP,\OPH, \TIME} :: \PENDING, \ACCEPTED, \MANAGERS,
      \CONTRACTORS, \TIME']}
    \BlockTrans 
    { % [\EC{\RAISE timeout}  :: \EXPRS, \ACCOUNTS, \OPERATIONS] \|
      [\PENDING, \ACCEPTED, \UPDATECOU(\MANAGERS, \PUK, \FALSE),
      \CONTRACTORS, \TIME']}
  }
\end{mathpar}

@@

\iffalse 
\begin{mathpar}

 \inferrule[Node-Op]
  {
    \Angle{\PAK,\OP.\PUK} \in \ACCOUNTS
  }{
    [\EXPRS, \ACCOUNTS, \OPERATIONS]
    \NodeTrans{}
    [\EXPRS, \ACCOUNTS, \OP:: \OPERATIONS]
  }

  \inferrule[Node-Oph]
  {
   \\
  }{
    [\EC\OP :: \EXPRS, \ACCOUNTS, \OPERATIONS]
    \NodeTrans{}
    [\EC\OPH :: \EXPRS, \ACCOUNTS, \OPERATIONS]
  }
\end{mathpar}
\fi

\begin{mathpar}
  \inferrule[Node-System]
  {\NODE \NodeTrans \NODE'}
  { {\NODE :: \overline\NODE \| \BLOCKCHAIN}
    \SystemTrans
    {\NODE' :: \overline\NODE \| \BLOCKCHAIN}}

@@

\subsection{Transfers}
\iffalse 
Rule 1 [injected]:

\begin{mathpar}
  \inferrule{
    \CHECKBAL (\MANAGERS, \PUK, \NTEZ, \MTEZ) \\
    \CHECKCOU (\MANAGERS, \PUK) \\
    \CHECKPUB (\MANAGERS, \PUK') \\
    \CHECKGAS (\PUK, \PUK', \NTEZ, \MTEZ) \\
    \OP = \TRANSFER\NTEZ\PUK{\PUK'}\MTEZ \\
    \OPH = \GENERATEOPH (\PUK, \PUK', \NTEZ, \MTEZ, \TIME)
  }{
   { [\ACCOUNTS, \OP :: \OPERATIONS] \| [\PENDING,
     \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME] } \SystemTrans \\
   { [\EXPRS, \ACCOUNTS, \OPERATIONS] \|
     [ \Angle{\OP,\OPH, \TIME}
     ::\PENDING,
     \ACCEPTED,
     \UPDATECOU(\MANAGERS, \PUK, \TRUE),
     \CONTRACTORS,
     \TIME]
   }
  }
\end{mathpar}
~\\
~\\
\fi
Rule 1 [rejected of counter]:
\begin{mathpar}
  \inferrule{
    %\NEG\ \CHECKCOU (\MANAGERS, \PUK)\\
    %\OP = \TRANSFER\NTEZ\PUK{\PUK'}\MTEZ \\
    \NEG\ \CHECKCOU (\MANAGERS, \PUK) \\
    \OP = \TRANSFER\NTEZ\PUK{\PUK'}\MTEZ \\
  }{
   { [\EXPRS, \ACCOUNTS, (\EC{},\OP) :: \OPERATIONS] \| [\PENDING,
     \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME] } \SystemTrans
   { [\EXPRS, \ACCOUNTS, \OPERATIONS] \|
     [ \PENDING,
     \ACCEPTED,
     \MANAGERS,
     \CONTRACTORS,
     \TIME]
   }
  }
\end{mathpar}
~\\
~\\
Rule 2 [rejected of balance]:
\begin{mathpar}
  \inferrule{
    \NEG\ \CHECKBAL (\MANAGERS, \PUK, \NTEZ, \MTEZ) \\
    \OP = \TRANSFER\NTEZ\PUK{\PUK'}\MTEZ \\
  }{
   { [\EXPRS, \ACCOUNTS, (\EC{},\OP) :: \OPERATIONS] \| [\PENDING,
     \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME] } \SystemTrans
   { [\EXPRS, \ACCOUNTS, \OPERATIONS] \|
     [ \PENDING,
     \ACCEPTED,
     \MANAGERS,
     \CONTRACTORS,
     \TIME]
   }
  }
\end{mathpar}
~\\
~\\
Rule 3 [rejected of public key]:
\begin{mathpar}
  \inferrule{
    \NEG\ \CHECKPUB (\MANAGERS, \PUK') \\
    \OP = \TRANSFER\NTEZ\PUK{\PUK'}\MTEZ \\
  }{
   { [\EXPRS, \ACCOUNTS, (\EC{},\OP) :: \OPERATIONS] \| [\PENDING,
     \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME] } \SystemTrans
   { [\EXPRS, \ACCOUNTS, \OPERATIONS] \|
     [ \PENDING,
     \ACCEPTED,
     \MANAGERS,
     \CONTRACTORS,
     \TIME]
   }
  }
\end{mathpar}
~\\
~\\
Rule 4 [rejected of fee]:
\begin{mathpar}
  \inferrule{
    \NEG\ \CHECKGAS (\PUK, \PUK', \NTEZ, \MTEZ) \\
    \OP = \TRANSFER\NTEZ\PUK{\PUK'}\MTEZ \\
  }{
   { [\EXPRS, \ACCOUNTS, (\EC{},\OP) :: \OPERATIONS] \| [\PENDING,
     \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME] } \SystemTrans
   { [\EXPRS, \ACCOUNTS, \OPERATIONS] \|
     [ \PENDING,
     \ACCEPTED,
     \MANAGERS,
     \CONTRACTORS,
     \TIME]
   }
  }
\end{mathpar}
\iffalse 
Rule 6 [included]:
\begin{mathpar}
  \inferrule[Block-Accept]{
    \OP = \TRANSFER\NTEZ\PUK{\PUK'}\MTEZ \\
    \TIME'-\TIME < 60
  }{
    {[\Angle{\OP,\OPH, \TIME} :: \PENDING, \ACCEPTED, \MANAGERS,
      \CONTRACTORS, \TIME']}
    \BlockTrans  \\
    {[\PENDING, \Angle{\OP,\OPH, \TIME,\TIME'} :: \ACCEPTED,
      \UPDATESUCC(\MANAGERS, \PUK, \PUK', \NTEZ, \MTEZ),
      \CONTRACTORS, \TIME'+1]}
  }
\end{mathpar}
Rule 7 [timeout]: (applies to both, implicit transfers and contract invocations)
\begin{mathpar}
  \inferrule[Block-Timeout]{
    \OP = \TRANSFER[\STRING]\NTEZ\PUK\ADDR\MTEZ \\
    \TIME'-\TIME \ge 60
  }{
    {[\Angle{\OP,\OPH, \TIME} :: \PENDING, \ACCEPTED, \MANAGERS,
      \CONTRACTORS, \TIME']}
    \BlockTrans
    {[\PENDING, \ACCEPTED, \UPDATECOU(\MANAGERS, \PUK, \FALSE),
      \CONTRACTORS, \TIME']}
  }
\end{mathpar}
\fi
\subsection{Smart Contracts}
A. Originate
~\\
~\\
Rule 1 [injected]:

\begin{mathpar}
  \inferrule[Block-Originate]{
    \CHECKBAL (\MANAGERS, \PUK, \NTEZ, \MTEZ) \\
    \CHECKCOU (\MANAGERS, \PUK) \\
    \CHECKGAS (\CODE, \INIT, \NTEZ, \MTEZ)  \\
    \CHECKPRG (\CODE, \STRING) \\\\
    \OP = \ORIGINATE\NTEZ\PUK\CODE\STRING\MTEZ \\
    \OPH = \GENERATEOPH(\PUK, \CODE, \NTEZ, \MTEZ, \STRING,\TIME) 
  }{
    [\EXPRS, \ACCOUNTS, (\EC{},\OP) :: \OPERATIONS
      ] \| [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME] \to \\
    [\EC{\OPH}  :: \EXPRS, \ACCOUNTS, \OPERATIONS] \|
      [\Angle{\OP, \OPH,\TIME} :: \PENDING, \ACCEPTED, \UPDATECOU(\MANAGERS,\PUK,\TRUE), \CONTRACTORS, \TIME]
  }
\end{mathpar}
~\\
~\\
Rule 2 [rejected of code]:
\begin{mathpar}
  \inferrule{
    \NEG\ \CHECKPRG (\CODE, \STRING) \\
    \OP = \ORIGINATE\NTEZ\PUK\CODE\STRING\MTEZ
  }{
    [
     \EXPRS, \ACCOUNTS, (\EC{},\OP) :: \OPERATIONS
      ] \| [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME] \to 
    [\EXPRS, \ACCOUNTS, \OPERATIONS] \|
      [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]
  }
\end{mathpar}
~\\
~\\
Rule 3 [rejected of counter]:
\begin{mathpar}
  \inferrule{
    \NEG\ \CHECKCOU (\MANAGERS, \PUK) \\
    \OP = \ORIGINATE\NTEZ\PUK\CODE\STRING\MTEZ
  }{
    [
      \EXPRS, \ACCOUNTS, (\EC{},\OP) :: \OPERATIONS
      ] \| [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME] \to
    [\EXPRS, \ACCOUNTS, \OPERATIONS] \|
      [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]
  }
\end{mathpar}
~\\
~\\
Rule 4 [rejected of balance]:
\begin{mathpar}
  \inferrule{
    \NEG\ \CHECKBAL (\MANAGERS, \PUK, \NTEZ, \MTEZ) \\
    \OP = \ORIGINATE\NTEZ\PUK\CODE\STRING\MTEZ
  }{
    [
      \EXPRS, \ACCOUNTS, (\EC{},\OP) :: \OPERATIONS
      ] \| [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME] \to 
    [\EXPRS, \ACCOUNTS, \OPERATIONS] \|
      [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]
  }
\end{mathpar}
~\\
~\\
Rule 5 [rejected of fee]:
\begin{mathpar}
  \inferrule{
    \NEG\ \CHECKGAS (\CODE, \INIT, \NTEZ, \MTEZ) \\
    \OP = \ORIGINATE\NTEZ\PUK\CODE\STRING\MTEZ
  }{
    [
      \EXPRS, \ACCOUNTS, (\EC{},\OP) :: \OPERATIONS
      ] \| [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME] \to 
    [\EXPRS, \ACCOUNTS, \OPERATIONS] \|
      [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]
  }
\end{mathpar}

~\\
~\\
Rule 6 [included]:
\begin{mathpar}
  \inferrule[Block-Accept]{
    \OP = \ORIGINATE\NTEZ\PUK\CODE\STRING\MTEZ \\
    \TIME'-\TIME < 60
  }{
      [\Angle{\OP, \OPH,\TIME} :: \PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME']
    \SystemTrans
      [\PENDING, \Angle{\OP, \OPH,\TIME,\TIME'} ::  \ACCEPTED, \UPDATESUCC
      (\MANAGERS, \PUK, \NTEZ, \MTEZ), \\ \Angle{\GENERATEHASH(\CODE, \INIT, \TIME, \TIME'), \NTEZ, \CODE, \STRING} :: \CONTRACTORS, \TIME'+1]
  }
\end{mathpar}
~\\
~\\
Rule 7 [timeout]:
\begin{mathpar}
  \inferrule[Block-Timeout]{
    \OP = \ORIGINATE\NTEZ\PUK\CODE\STRING\MTEZ \\
    \TIME'-\TIME \ge 60
}{
      [\Angle{\OP, \OPH,\TIME} :: \PENDING, \ACCEPTED, \MANAGERS,
      \CONTRACTORS, \TIME']  
      \BlockTrans \    
      [\Angle{\OP, \OPH,\TIME} :: \PENDING, \ACCEPTED, \MANAGERS,
      \CONTRACTORS, \TIME'] 
  }

@@

  }{[\EXPRS, \ACCOUNTS, (\EC{},\OP) :: \OPERATIONS] \|

@@

    [\EC{\OPH}  :: \EXPRS, \ACCOUNTS, \OPERATIONS] \|

@@

    [\EXPRS, \ACCOUNTS, \OPERATIONS] \|

@@

    \NodeTrans\ [\epsilon[\BAL] ::\EXPRS, \ACCOUNTS, \OPERATIONS]  \| \BLOCKCHAIN}

@@

    \NodeTrans\ [\epsilon[\STORAGE] ::\EXPRS, \ACCOUNTS, \OPERATIONS]  \| \BLOCKCHAIN}

@@

    \NodeTrans\ [\epsilon[\CODE] ::\EXPRS, \ACCOUNTS, \OPERATIONS]  \| \BLOCKCHAIN}

@@

    \NodeTrans\ [\epsilon[\COU] ::\EXPRS, \ACCOUNTS, \OPERATIONS]  \| \BLOCKCHAIN}

@@

Query 6 [fail of a query for an account]:
    \NEG\ \CHECKPUB (\MANAGERS, \PUK) \
  }{[\epsilon[\GETBALANCE\PUK/\GETCOUNTER\PUK] :: \EXPRS, \ACCOUNTS, \OPERATIONS]  \| [\PENDING, \ACCEPTED,  \MANAGERS, \CONTRACTORS, \TIME]
    \NodeTrans\\ [\epsilon[\FAIL] ::\EXPRS, \ACCOUNTS, \OPERATIONS]  \| [\PENDING, \ACCEPTED,  \MANAGERS, \CONTRACTORS, \TIME]}
Query 7 [fail of a query for an account]:
    \NEG\ \CHECKPUB (\CONTRACTORS, \PUH) 
  }{[\epsilon[\GETBALANCE\PUH/\GETSTORAGE\PUH/\GETCODE\PUH] :: \EXPRS, \ACCOUNTS, \OPERATIONS]  \| [\PENDING, \ACCEPTED,  \MANAGERS, \CONTRACTORS, \TIME]
    \NodeTrans\\ [\epsilon[\FAIL] ::\EXPRS, \ACCOUNTS, \OPERATIONS]  \| [\PENDING, \ACCEPTED,  \MANAGERS, \CONTRACTORS, \TIME]}
Query 8 [status-pending]:

@@

      [\Angle{\OP, \OPH, \TIME'} :: \PENDING, \ACCEPTED,  \MANAGERS, \CONTRACTORS, \TIME]

@@

    \NodeTrans\ [\epsilon[\STATUSPENDING] ::\EXPRS, \ACCOUNTS, \OPERATIONS]  \| \BLOCKCHAIN}

@@

Query 9 [status-including]:

@@

      [\PENDING, \Angle{\OP, \OPH, \TIME', \TIME''} :: \ACCEPTED,  \MANAGERS, \CONTRACTORS, \TIME] \\
    $n$ = \TIME\ - \TIME''

@@

    \NodeTrans\ [\epsilon[\STATUSINCLUDING($n$)] ::\EXPRS, \ACCOUNTS, \OPERATIONS]  \| \BLOCKCHAIN}

@@

Query 10 [status-timeout]:
    \NEG\ \CHECKEXIST (\ADDR, \PENDING, \ACCEPTED)
  }{[\epsilon[\GETSTATUS\OPH] :: \EXPRS, \ACCOUNTS, \OPERATIONS]  \| [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]
    \NodeTrans\ [\epsilon[\STATUSTIMEOUT] ::\EXPRS, \ACCOUNTS, \OPERATIONS]  \| [\PENDING, \ACCEPTED, \MANAGERS, \CONTRACTORS, \TIME]}
\section{Functions}
\begin{enumerate}
    \item Function \CHECKPUB (\PUK, \MANAGERS)\ checks whether a public key \PUK\ exists in \MANAGERS.
    \item Function \CHECKPUH (\PUH, \CONTRACTORS)\ checks whether a public hash \PUH\ exists in \CONTRACTORS.
    \item Function \CHECKBAL (\MANAGERS, \PUK, \NTEZ, \MTEZ) checks whether the balance of the account that associates with the public key \PUK\ is greater or equal to \NTEZ\ plus \MTEZ.
    \item Function \CHECKCOU (\MANAGERS, \PUK)\ checks whether the current counter of an account that associates with the public key \PUK\ is unlocked (its flag is False).
    \item Function \CHECKEXIST (\ADDR, \PENDING, \ACCEPTED)\ checks whether an address  \ADDR\ exists in either \PENDING\ or \ACCEPTED.
    \item Function \UPDATESUCC(\MANAGERS, \PUK, \PUK', \NTEZ, \MTEZ) updates the balance and the counter of the account that associates with the public key \PUK\ and the balance of the account that associates with the public key \PUK', where
    \begin{itemize}
